### 2016-10-04 FrontBackmatter/Acknowledgments.tex
Adjust equations

It has not been one day, it's been four years.\footnotetext{
Just a perfect day \\
You made me forget myself \\
I thought I was \\
Someone else, someone good \\
\hspace*{15pt}
--- \textsc{Lou Reed}}
And it's not always been perfect.
It is however true that the people I have met and interacted with during
this adventure have made me feel \emph{someone good}.
I don't feel it's an exaggeration to say that if I have made it this far
is also because of \emph{you}.
Thus, these few, poorly written lines are
a \emph{dedication} of this dissertation to you
and an \emph{acknowledgment}
of the patience and love you have shown towards me.
Thanks for not giving up on me.

@@

in no particular order:\footnotetext{
And all of my friends were there, \\
and no one cared \\
\hspace*{15pt}
--- \textsc{The Kinks}}
\begin{itemize}
  \item To \emph{Radovan Bast}, \emph{il miglior fabbro},
  \item To \emph{Davide Michetti}, the inventor of nicknames,
  \item To \emph{The Little Lebowski Urban Achievers}, Erlend, Ana and
    Torgeir,
  \item To the \emph{Schrodinger killed my cat!}
\end{itemize}

>>>>

It has not been one day, it's been four years.\footnotetext{Just a perfect day \\
You made me forget myself \\
I thought I was \\
Someone else, someone good \\
\hspace*{15pt}
--- \textsc{Lou Reed}}
And it's not always been perfect.
It is however true that the people I have met and interacted with during
this adventure have made me feel \emph{someone good}.
I don't feel it's an exaggeration to say that if I have made it this far
is also because of \emph{you}.
Thus, these few, poorly written lines are
a \emph{dedication} of this dissertation to you
and an \emph{acknowledgment}
of the patience and love you have shown towards me.
Thanks for not giving up on me.

@@

in no particular order:\footnotetext{And all of my friends were there, \\
and no one cared \\
\hspace*{15pt}
--- \textsc{The Kinks}}
\begin{itemize}
  \item To \emph{Radovan Bast}, \emph{il miglior fabbro},
  \item To \emph{Davide Michetti}, the inventor of nicknames,
  \item To \emph{The Little Lebowski Urban Achievers}, Erlend, Ana and
    Torgeir,
  \item To the \emph{Schrodinger killed my cat!}
\end{itemize}

\textitalian{A Grazia, Graziella e al Toblerone, qualcuno sa perché.}

### 2016-10-04 FrontBackmatter/Introduction.tex
Adjust equations

\section*{What Are the Electrons Really Doing in Molecules?}\footnotetext{
[...] \textnorsk{og fordi jeg alltid har hatt en dragning mot det skjulte og hemmelige.}
\\
\hspace*{15pt}
--- \textnorsk{\textsc{K. O. Knausgård}, \textit{Om Høsten}}
}

>>>>

\section*{What Are the Electrons Really Doing in Molecules?}\footnotetext{[...] \textnorsk{og fordi jeg alltid har hatt en dragning mot det skjulte og hemmelige.}
\\
\hspace*{15pt}
--- \textnorsk{\textsc{Karl Ove Knausgård}, \\ \hspace*{25pt} \textit{Om Høsten}}
}
